---
title: "Understanding the grid structure"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Understanding the grid structure}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
```{r setup, warning = FALSE, message = FALSE}
library(hexmap)
library(sf)
library(ggplot2)
```

Consider a map with boundaries $(x_1, y_1, x_2, y_2)$ such that 

* $x_1$ and $x_2$ denote the minimum and maximum longitude of the map, respectively,
* $y_1$ and $y_2$ denote the minimum and maximum latitude of the map, respectively,
* $A = (y_2 - y_1)(x_2 - x_1)$ is the total area of the map,
* $L$ is the total land area of the map,
* $n_{xe}$ and $n_{xo}$ is the total number of hexagons on even and odd rows respectively,
* $n_{ye}$ and $n_{yo}$ is the total number of hexagons on even and odd columns respectively,
* $n_r$ and $n_c$ are the maximum number of rows and columns in the grid structure,
* $n$ is the desired total number of hexagons,
* $c$ is the cell size, which is the same as the width of the non-flat topped hexagon. 
 
We assume that the hexagon is not flat topped. Note that $A$, $L$, $n$, $x_1$, $x_2$, $y_1$ and $y_2$ are known.


```{r}
square <- matrix(c(0, 0, 
                   0, 1, 
                   1, 1, 
                   1, 0, 
                   0, 0), 
                 ncol = 2, 
                 byrow = TRUE) %>% 
  list() %>% 
  st_polygon()

plot_hex_tile <- function(cellsize) {
  ggplot(st_make_grid(square, cellsize = cellsize, square = FALSE)) +
  geom_sf(fill = "transparent") + 
  geom_sf(data = square, fill = "transparent", color = "red") +
  ggtitle(paste("Cell size = ", cellsize))
}

plot_hex_tile(0.25)
plot_hex_tile(0.5)
plot_hex_tile(1)

```

